Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-27 parts/summary.tex
time thing

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{img/timelapse}
  \caption{Activity of volunteers; amount of models, summed over all candidates, after the first model was generated. 8 users contributed more than five models. vertical lines show 1 minute, one hour, one day, one week, one month, one year, two years. Dashed vertical line shows the start of the SW01 modelling challenge.}
  \label{fig:time}
\end{figure}
